Changes in the justification of educational inequalities. The role of perceptions of inequality and meritocracy during the COVID pandemic.

### 2025-01-21 submit/blinded-paper.tex
add submit archives

\includegraphics[width=0.85\textwidth,height=\textheight]{output/graphs/merit_plot.png}

@@

\begin{longtable}[]{@{}l@{}}
\caption{Independent variables}\label{tbl-descriptives}\tabularnewline
\toprule\noalign{}
\endfirsthead
\endhead
\bottomrule\noalign{}
\endlastfoot
\includegraphics{output/tables/desc02.png} \\
\end{longtable}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{output/graphs/alluvial_dep.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{output/graphs/years_plot.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{output/graphs/corr.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{paper_files/figure-pdf/fig-interact-talent-1.pdf}

>>>>

\includegraphics[width=0.85\textwidth,height=\textheight]{merit_plot-rr.png}

@@

\begin{longtable}[]{@{}l@{}}
\caption{Independent variables}\label{tbl-descriptives}\tabularnewline
\toprule\noalign{}
\endfirsthead
\endhead
\bottomrule\noalign{}
\endlastfoot
\includegraphics{desc02-rr.png} \\
\end{longtable}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{alluvial_dep-rr.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{years_plot-rr.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{corr-rr.png}

@@

\includegraphics[width=0.85\textwidth,height=\textheight]{fig-interact-talent-1.pdf}
